Multisensor Architecture for an Intersection Management System

### 2015-03-25 ch2-mdf_ims.tex
IMS components graph relocated
Enhanced first part of section IMS

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.175]{fig/2/ims_graph.png}
\caption{Fusion algorithms based on level of fusion. (from \cite{Luo2011})}
\label{fusionAlgs}
\end{figure}

@@

Different types of applications and systems are conceived to address these issues. Some tasks those systems realize are intersection monitoring, vehicles detection, incident warning, collision avoidance, among others. Communication approaches in these systems are based in the interaction between vehicles and infrastructure, commonly divided in three groups: Vehicle-to-vehicle communication (V2V) , Vehicle-to-infrastructure communication (V2I) and the combination of both of them (V2X).

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.75]{fig/2/fig1}
\caption{Generic block diagram of an Intersection Management System (from \cite{Chan2005}).}
\label{arch}
\end{figure}

Figure \ref{arch}, presents a generic block diagram of an Intersection Management System composed by three main components: (a) Data source, that could be infrastructure sensors, like inductive loops, range sensors or cameras, and also could be vehicle sensors. (b) Decision system, which is the core of the whole system, is in charge of analyse and process information provided by infrastructure, vehicles and environment in order to predict future incidents, control traffic and generate safe decisions and warnings alerts. Finally, (c) is the presentation and displaying of the output of decision system. It could be at the infrastructure using dynamic signals, semaphore controlling, or vehicle-directed through on-board visualization/notification system.

@@

\subsection{Applications in IMS}

@@

%\subsection{Intersection Management Systems and Multisensor Data Fusion}

>>>>

@@

Different types of applications and systems are conceived to address these issues. Some tasks performed by those are intersection monitoring, vehicles detection, incident warning, collision avoidance, among others. A typical Intersection Management System is composed by three main components: Data source, that could be infrastructure sensors, like inductive loops, range sensors or cameras, along vehicle sensors and traveling data; decision system, which is the core of the whole system, is in charge of analyse and process information provided by infrastructure, vehicles and authorities in order identify objects, recognise patterns, predict future incidents, control traffic and generate safe decisions and warnings alerts; and finally, is the presentation and displaying of the output of decision system, through infrastructure using dynamic signals, semaphore controlling, or using direct communication with drivers or vehicles through on-board visualisation/notification system. A block diagram of a generic IMS is presented in figure \ref{arch}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.55]{fig/2/genericIMS.png}
\caption{Generic block diagram of an Intersection Management System.}
\label{arch}
\end{figure}

@@

\subsection{Components in IMS application}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.2125]{fig/2/ims_graph2.png}
\caption{Components of an interesection management system application.}
\label{fusionAlgs}
\end{figure}

@@

\subsection{Developments in Intersection Management Systems}
